Make any stupid plot you want

### 2021-01-15 draft/sections/math.tex
trying to rework to get a good scatter + gotta encode them all as motivation
changed all the file paths

%%close out the fiber bundle section with the cartesian products, which gives us heterogenous data , univariate to multivariate. We can decompose the fiber bundle to components bundles \pi:E_1\rightarrow K, .... \pi: E_n\rightarrow K
\subsubsection{Connectivity of the Data} 
%% flows out of the fiber section into, now gluing observations together into a thing
%% can then put functions on edges/planes/etc so we have true continouity
\label{sec:base_data}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/sections/math/k_different_types.png}
    \label{fig:base_space_types}
    \caption{The topological base space $K$ encodes the connectivity of the data space, for example if the data is independent points or a map or on a sphere}
\end{figure}

@@

\begin{figure}[H]
    \label{fig:base_space_div}
    \includegraphics[width=.5\linewidth]{figures/sections/math/k_qspace.png}
    %%include second figure where fiber goes otherway
\end{figure}
The topology $K$ and the

@@

\subsubsection{Data: Section}
\label{sec:section_data}
The sections of the fiber bundles are the instances of the data. They are the functions that map from a point $k \in K$ to a set of values in $F$. For example, if we have a database, the section is the table that yields a row given an index. The section $\tau$ is the mapping from base space to total space $\tau: K\rightarrow E$ 
\begin{equation}
    \label{eq:section}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[d, "\pi"']           \\
        & K \arrow[u, "\tau"', bend right]
    \end{tikzcd}
\end{equation}

@@

\begin{figure}[H]
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/sections/math/temp_1k.png}
        %% add box around neighboring P and Map
        \label{fig:base_example_line}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/sections/math/temp_2k.png}
        \label{fig:base_example_plane}
    \end{subfigure}
    \label{fig:base_example}
    \caption{These two datasets have the same fiber of temperature but different base spaces. In figure~\ref{fig:base_example_line} the temperature values are 1D continuous, while in figure~\ref{fig:base_example_plane} the temperature values are 2D continuous.}
\end{figure}

@@

\begin{figure}[H]
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/sections/math/temp_2f.png}
        \label{fig:fiber_example_plane}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/sections/math/temp_3f.png}
        \label{fig:fiber_example_cube}
    \end{subfigure}
    \label{fig:fiber_example}
    \caption{The fiber is expanded to include metadata fields that describe the semantics of $K$. In figure~\ref{fig:fiber_example_plane} the fiber is \textrm{temperature} $\times$ \textrm{time} and in figure~\ref{fig:fiber_example_cube} the fiber is \textrm{temperature}$\times$ \textrm{latitude} $\times$ {longitude}}.
\end{figure}

@@

\begin{figure}[H]
    \includegraphics[width=1\linewidth]{figures/sections/math/fiberbundle.png}
    \label{fig:fiber_example_section}
    \caption{The section $\tau_1$ returns the blue points,  while $\tau_2$ returns the purple points. $\Gamma(E)$ is the set of all sections, including $\tau_1$ and $\tau_2$}.  
\end{figure}
Given the fiber described in equation~\ref{eq:fiber_plane}, the sections $\tau_{1}$ and $\tau_{2}$ in figure~\ref{fig:fiber_example_section} return tuples of the form
\begin{equation}
\tau(k) = (k, (temperature, time))
\end{equation}
such that sections with the constraint that time is monotonic return a timeseries.

@@

\subsubsection{{Example}}
\begin{figure}[H]
    \includegraphics[width=.4\linewidth]{figures/sections/math/render.png}
    \caption{}
    \label{fig:render}
\end{figure}

@@

\subsubsection{Assembling Marks}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/sections/math/path_of_q}
    \label{fig:artist_q}
    \caption{The $\nu$ functions convert data $E$ to visual $V$. $Q$ assembles the different types of visual parameters $V_{i}$ into a graphic in $H$. $Q\circ\mu(\xi^{-1}J)$ forms a visual mark by applying $Q$ to a region mapped to connected components $J \subset K$.}  
\end{figure}

@@

\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/sections/math/diff_type_q.png}
    \label{fig:artist_mark_change}
\end{figure}

@@

\begin{figure}[H]
    \label{fig:simplex}
    \includegraphics{figures/sections/math/simplex.png}
    \caption{Simplices can encode the connectivity of the data, from fully disconnected (0 simplex) observations to all observations are connected to at least 3 other observations}
\end{figure}

>>>>

%%close out the fiber bundle section with the cartesian products, which gives us heterogenous data , univariate to multivariate. We can decompose the fiber bundle to components bundles \pi:E_1\rightarrow K, .... \pi: E_n\rightarrow K
\subsubsection{Connectivity: Base Space} 
%% flows out of the fiber section into, now gluing observations together into a thing
%% can then put functions on edges/planes/etc so we have true continouity

\label{sec:base_data}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/k_different_types.png}
    \label{fig:base_space_types}
    \caption{The topological base space $K$ encodes the connectivity of the data space, for example if the data is independent points or a map or on a sphere}
\end{figure}

@@

\begin{figure}[H]
    \label{fig:base_space_div}
    \includegraphics[width=.5\linewidth]{figures/math/k_qspace.png}
    %%include second figure where fiber goes otherway
\end{figure}
The topology $K$ and the

@@

\subsubsection{Data: Section}
%%% visual variable encoding in a consistent/atomic way in a complex strcutrue 
\label{sec:section_data}
The sections of the fiber bundles are the instances of the data. They are the functions that map from a point $k \in K$ to a set of values in $F$. For example, if we have a database, the section is the table that yields a row given an index. The section $\tau$ is the mapping from base space to total space $\tau: K\rightarrow E$ 
\begin{equation}
    \label{eq:section}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[d, "\pi"']           \\
        & K \arrow[u, "\tau"', bend right]
    \end{tikzcd}
\end{equation}

@@

\begin{figure}[H]
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_1k.png}
        %% add box around neighboring P and Map
        \label{fig:base_example_line}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_2k.png}
        \label{fig:base_example_plane}
    \end{subfigure}
    \label{fig:base_example}
    \caption{These two datasets have the same fiber of temperature but different base spaces. In figure~\ref{fig:base_example_line} the temperature values are 1D continuous, while in figure~\ref{fig:base_example_plane} the temperature values are 2D continuous.}
\end{figure}

@@

\begin{figure}[H]
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_2f.png}
        \label{fig:fiber_example_plane}
    \end{subfigure}
    \begin{subfigure}{.5\textwidth}
        \includegraphics[width=\textwidth]{figures/math/temp_3f.png}
        \label{fig:fiber_example_cube}
    \end{subfigure}
    \label{fig:fiber_example}
    \caption{The fiber is expanded to include metadata fields that describe the semantics of $K$. In figure~\ref{fig:fiber_example_plane} the fiber is \textrm{temperature} $\times$ \textrm{time} and in figure~\ref{fig:fiber_example_cube} the fiber is \textrm{temperature}$\times$ \textrm{latitude} $\times$ {longitude}}.
\end{figure}

@@

\begin{figure}[H]
    \includegraphics[width=1\linewidth]{figures/math/fiberbundle.png}
    \label{fig:fiber_example_section}
    \caption{The section $\tau_1$ returns the blue points,  while $\tau_2$ returns the purple points. $\Gamma(E)$ is the set of all sections, including $\tau_1$ and $\tau_2$}.  
\end{figure}
Given the fiber described in equation~\ref{eq:fiber_plane}, the sections $\tau_{1}$ and $\tau_{2}$ in figure~\ref{fig:fiber_example_section} return tuples of the form
\begin{equation}
\tau(k) = (k, (temperature, time))
\end{equation}
such that sections with the constraint that time is monotonic return a timeseries.

@@

\subsubsection{{Example}}
\begin{figure}[H]
    \includegraphics[width=.4\linewidth]{figures/math/render.png}
    \caption{}
    \label{fig:render}
\end{figure}

@@

\subsubsection{Assembling Marks}
\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/path_of_q}
    \label{fig:artist_q}
    \caption{The $\nu$ functions convert data $E$ to visual $V$. $Q$ assembles the different types of visual parameters $V_{i}$ into a graphic in $H$. $Q\circ\mu(\xi^{-1}J)$ forms a visual mark by applying $Q$ to a region mapped to connected components $J \subset K$.}  
\end{figure}

@@

\begin{figure}[H]
    \includegraphics[width=\textwidth]{figures/math/diff_type_q.png}
    \label{fig:artist_mark_change}
\end{figure}

@@

\begin{figure}[H]
    \label{fig:simplex}
    \includegraphics{figures/math/simplex.png}
    \caption{Simplices can encode the connectivity of the data, from fully disconnected (0 simplex) observations to all observations are connected to at least 3 other observations}
\end{figure}
